Empirical Analysis of the Role of Energy in Economic Growth

### 2013-01-28 EconGrowth.Rnw
Adjusted the formatting of the factors of production graph slightly to highlight the k and l lines as opposed to the energy lines.

\author[Calvin]{Caleb Reese}
\author[Calvin]{Lucas Timmer}
\author[Calvin]{Matthew Kuperus Heun \corref{cor1}}
\ead{mkh2@calvin.edu, tel: +1 (616) 526-6663, fax: +1 (616) 526-6501}

@@

<<setup, include=FALSE>>=
require(knitr)
require(lattice)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=FALSE)
opts_chunk$set(
  tidy=FALSE,
  fig.width=6,
  fig.height=4,
#  out.width=".45\\textwidth",
#  out.height=".38\\textwidth",
  comment=NA)

@@

<<Factors Lattice Graph, fig.width=6.5, fig.height=7.5, fig.cap="Factors of Production for All Countries. (China's indexed capital stock rises to $k = 9.2$ in 2011.)", echo=FALSE>>=
createFactorsLatticeGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(1, 1, 1, 1, 1) #line widths
  colors <- c("black", "black", "black", "black", "black") #line and point colors
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
                  index.cond=list(c(7,6,3,1,8,5,4,2,9)), #orders the panels. Default is alphabetical.
                  as.table=TRUE,
                  type=graphType,
                  layout=c(3,3),
                  par.settings = list(superpose.line = lineSpec),
                  key=list(text=list(c("k", "l", "q", "x", "u")),
                           type=graphType,
                           cex=0.85,
                           lines=lineSpec,
                           columns=1, x=0.01, y=0.95),
                  scales=list(cex=0.75, #controls text size on scales
                              tck=-0.5, #controls tick mark length
                              y=list(at=c(1,2,3,4,5,6,7,8,9,10))), 
                  xlab="",
                  ylim=c(0.5,4.5),
                  ylab="Indexed (1980=1 or 1991=1)")
  return(graph)
}
createFactorsLatticeGraph("All") #Reads data from the "AllData.txt" file.
@

<<Country Factors Graph, echo=FALSE>>=
createCountryFactorsGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(1, 1, 1, 1, 1) #line widths
  colors <- c("black", "black", "black", "black", "black") #line and point colors
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year, data=dataTable,
                  type=graphType,
                  par.settings = list(superpose.line = lineSpec),
                  key=list(text=list(c("k", "l", "q", "x", "u")),
                           type=graphType,
                           lines=lineSpec,
                           columns=1, x=0.0, y=0.98),
                  scales=list(cex=1.0, #controls text size on scales
                              tck=-0.5), #controls tick mark length
                  ylab="Indexed (1980=1)")
  return(graph)
}
@

@@

@@

cobbDouglasParamsTable <- function(){
  dataCD <- rbind(cobbDouglasCountryRow("US"),
                cobbDouglasCountryRow("UK"),
                cobbDouglasCountryRow("JP"),
                cobbDouglasCountryRow("CN"),
                cobbDouglasCountryRow("ZA"),
                cobbDouglasCountryRow("SA"),
                cobbDouglasCountryRow("IR"),
                cobbDouglasCountryRow("TZ"),
                cobbDouglasCountryRow("ZM"))
  colnames(dataCD) <- c(" ", "$\\lambda$", " ", 
                        " ", "$\\alpha$",  " ",
                        " ", "$\\beta$",   " ")
  rownames(dataCD) <- countries
  tableCD <- xtable(dataCD, 
                    caption="Cobb-Douglas parameters for 1980-2011 (developed nations) or 1991-2011 (others). (Parameter estimates beneath symbol. 95\\% confidence bounds to left and right.)", 
                    digit = c(1, 4,4,4, 2,2,2, 2,2,2),
                    align = "r|ccc|ccc|ccc")
  return(tableCD)
}

####################################
# Creates a LaTeX printable table from the Cobb Douglas data. This function first calls cobbDouglasData.
#
# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
#
# returns a printable LaTeX table from xtable.
##
cobbDouglasCountryTable <- function(countryName){
  dataCD <- cobbDouglasData(countryName) 
  colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
  tableCD <- xtable(dataCD, caption=paste(countryName, " Cobb-Douglas, 1980-2011", sep=""), digit = c(4, 4, 2, 2, 1))
  #print(tableCD)
  return(tableCD)  
}
@

>>>>

\author[Calvin]{Caleb Reese}
\author[Calvin]{Lucas Timmer}
\author[Calvin]{Matthew Kuperus Heun\corref{cor1}}
\ead{mkh2@calvin.edu, tel: +1 (616) 526-6663, fax: +1 (616) 526-6501}

@@

<<setup, include=FALSE>>=
require(knitr)
require(lattice)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=FALSE)
opts_chunk$set(
  tidy=FALSE,
  fig.width=6,
  fig.height=4,
  comment=NA)

@@

<<Country Factors Graph, echo=FALSE>>=
createCountryFactorsGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(1, 1, 1, 1, 1) #line widths
  colors <- c("black", "black", "black", "black", "black") #line and point colors
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year, data=dataTable,
                  type=graphType,
                  par.settings = list(superpose.line = lineSpec),
                  key=list(text=list(c("k", "l", "q", "x", "u")),
                           type=graphType,
                           lines=lineSpec,
                           columns=1, x=0.0, y=0.98),
                  scales=list(cex=1.0, #controls text size on scales
                              tck=-0.5), #controls tick mark length
                  ylab="Indexed (1980=1)")
  return(graph)
}
@
<<Factors Lattice Graph, fig.width=6.5, fig.height=7.5, fig.cap="Factors of Production for All Countries. (China's indexed capital stock rises to $k = 9.2$ in 2011.)", echo=FALSE>>=
createFactorsLatticeGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  lineTypes <- c(1, 5, 2, 4, 3) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(2, 2, 1, 1, 1) #line widths
  colors <- c("black", "black", "red", "blue", "black") #line and point colors
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
                  index.cond=list(c(7,6,3,1,8,5,4,2,9)), #orders the panels. Default is alphabetical.
                  as.table=TRUE,
                  type=graphType,
                  layout=c(3,3),
                  par.settings = list(superpose.line = lineSpec),
                  key=list(text=list(c("k", "l", "q", "x", "u")),
                           type=graphType,
                           cex=0.85,
                           lines=lineSpec,
                           columns=1, x=0.01, y=0.95),
                  scales=list(cex=0.75, #controls text size on scales
                              tck=-0.5, #controls tick mark length
                              y=list(at=c(1,2,3,4,5,6,7,8,9,10))), 
                  xlab="",
                  ylim=c(0.5,4.5),
                  ylab="Indexed (1980=1 or 1991=1)")
  return(graph)
}
createFactorsLatticeGraph("All") #Reads data from the "AllData.txt" file.
@

@@

####################################
# Creates a LaTeX printable table from the Cobb Douglas data. This function first calls cobbDouglasData.
#
# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
#
# returns a printable LaTeX table from xtable.
##
cobbDouglasCountryTable <- function(countryName){
  dataCD <- cobbDouglasData(countryName) 
  colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
  tableCD <- xtable(dataCD, caption=paste(countryName, " Cobb-Douglas, 1980-2011", sep=""), digit = c(4, 4, 2, 2, 1))
  #print(tableCD)
  return(tableCD)  
}

@@

cobbDouglasParamsTable <- function(){
  dataCD <- rbind(cobbDouglasCountryRow("US"),
                cobbDouglasCountryRow("UK"),
                cobbDouglasCountryRow("JP"),
                cobbDouglasCountryRow("CN"),
                cobbDouglasCountryRow("ZA"),
                cobbDouglasCountryRow("SA"),
                cobbDouglasCountryRow("IR"),
                cobbDouglasCountryRow("TZ"),
                cobbDouglasCountryRow("ZM"))
  colnames(dataCD) <- c(" ", "$\\lambda$", " ", 
                        " ", "$\\alpha$",  " ",
                        " ", "$\\beta$",   " ")
  rownames(dataCD) <- countries
  tableCD <- xtable(dataCD, 
                    caption="Cobb-Douglas parameters for 1980-2011 (developed nations) or 1991-2011 (others). (Parameter estimates beneath symbol. 95\\% confidence bounds to left and right.)", 
                    digit = c(1, 4,4,4, 2,2,2, 2,2,2),
                    align = "r|ccc|ccc|ccc")
  return(tableCD)
}
@
